On particular examples of planar integral point sets and their classification \footnote{ This work was carried out at Voronezh State University and supported by the Russian Science Foundation grant 19-11-00197. }

### 2021-02-24 AvdMomZvolA_examples/ips_examples.tex
[AMZAE] Remove the remnants of estimates

where $n = 42$, $\operatorname{diam(\mathcal{P})} = 2473117504$. Using the ``blowing up''
construction, we obtain
\begin{equation}\label{result2}
d(m, 3m + 1) \leq 56
\end{equation}
The resulting estimate improves the estimate for $d(m, 3m)$, which is presented
in \cite{kemnitz1988punktmengen}. Figure~\ref{picture_12.pdf} shows an example
for $m = 3$.

@@

where $n = 46$, $\operatorname{diam(\mathcal{P})} = 3118278592$. Using the ``blowing up''
construction, we obtain
\begin{equation}\label{result3}
d(m, 4m + 1) \leq 1260
\end{equation}
Figure~\ref{picture_1260_R3.pdf} shows an example for $m = 3$.

>>>>

where $n = 42$, $\operatorname{diam(\mathcal{P})} = 2473117504$.

@@

where $n = 46$, $\operatorname{diam(\mathcal{P})} = 3118278592$.
